Points Above Replacement: A New NBA Metric to Evaluate Player Performance

### 2022-04-26 Manuscript/Manuscript.tex
Add files via upload

@@

Once all supporting statistics of PAR have been created, all that is left to 
do is combine them to achieve our PAR values for each player in the 
NBA. The formula for PAR is listed below.

@@

Equation~\ref{eq:PAR} gives a good idea of how many points a player 
accounts for 
during a 
game, how important that is for 
his given team, and how important it is compared to all other players. The 
last step is to standardize this 
PAR statistic, so that the mean is 0, and the standard deviation is 1. 
Logically, this helps the idea of the 
metric in the sense that a perfectly league average player should have a 
PAR of 0, and his presence or 
absence from his team neither adds nor subtracts value. Thus, we have 
created a new NBA player metric, 
Points Above Replacement, PAR. All of the calculations, multiple 
regression, and graphs were created using R \citep{R}.

@@

>>>>

\begin{equation}
\label{eq:TeamAdjustment}
  \frac{\text{Minutes Played}}{3456} \times
  \frac{\text{Points}}{\text{Team Total Points}}.
\end{equation}

Creating the ``Team Adjustment'' statistic via 
equation~\ref{eq:TeamAdjustment} has then successfully adjusted a 
player's statistics to his specific team.

@@

\begin{equation}
\label{eq:PointsPerWin}
 \frac{\text{Offensive Points} + \text{Defensive Points}} {\text{Minutes 
Played}} + 2160.
\end{equation}

By creating the ``Points Per Win'' statistic, equation~\ref{eq:PointsPerWin} 
has thus scaled down the statistic based 
on how many points are in an average win, similar to Runs Per Win in 
WAR. The constant of 2,160 would change to 2,460 for an 82-game 
season, for a typical NBA season.

Finally, once all supporting statistics of PAR have been created, all that is left to 
do is combine them to achieve our PAR values for each player in the 
NBA. The formula for PAR is listed below.

@@

Equation~\ref{eq:PAR} gives a good idea of how many points a player 
accounts for 
during a 
game, how important that is for 
his given team, and how important it is compared to all other players. The 
last step is to standardize this 
 rough PAR statistic, so that the mean is 0, and the standard deviation is 
1. 
Logically, this helps the idea of the 
metric in the sense that a perfectly league average player should have a 
PAR of 0, and his presence or 
absence from his team neither adds nor subtracts value. Thus, we have 
created a new NBA player metric, 
Points Above Replacement, PAR. All of the calculations, multiple 
regression, and graphs were created using R \citep{R}.

@@

The concept of assigning value to a player based on how many points he 
contributes to his team is the main goal of this statistic. By taking the 
calculation of WAR from baseball, which is how many wins a player 
contributes to his team, and adjusting it for the sport of basketball, and 
points rather than wins, it is felt that the goal is successfully achieved. The 
scaling of the data around the mean allows a ``replacement level'' player 
to contribute exactly 0 points to his team, and the rest of the league is 
compared to that. The team adjustment is a key one as well, as, 
depending on what team a player plays for, his value will change, 
sometimes even drastically. Further research would need to be done, 
such as comparing PAR's estimation with actual point differentials when 
an entire roster aside from a certain player plays, but for the most part, 
the original goal of creating this statistic is achieved.

As can be seen from the 
Table~\ref{tab:MultipleRegression}, it is in relative agreement with many 
other accepted statistics, and even takes some ideas from the calculation 
of those statistics. However, at the same time, it is unique enough that it 
introduces a brand new outlook to the advanced metrics subject. Other 
statistics look for other ways to value a player, which is where the 
variation comes into play, but for the most part, elite players are valued as 
such through PAR, which is how it is known that the statistic holds.

There are a few limitations to discuss in the calculation of PAR. Firstly, the 
subjectivity in calculating the coefficients for Offensive and Defensive 
Points, as seen in Table~\ref{tab:Coefficientstable}, could be changed to 
any numbers to serve whatever purpose one is looking for. However, in 
baseball's WAR, this is the subjective part of the statistic that causes 
there to realistically be many different kinds of WAR, despite them all 
being the same statistic. The coefficients could be tweaked to serve a 
number of different purposes. Further tests could also be done to test the 
validity of PAR in practice. This could help a final score estimation model 
in the future for the purpose of season simulations, sports betting, and a 
number of other purposes. The sample size of 1 season makes this 
difficult, so calculations across multiple seasons, and future ones would 
help this discussion. However, PAR seems to provide a decent estimate of 
a player's value to his team, which is especially shown through its relation 
to VORP and BPM, which are the advanced metrics with goals that are 
most similar to that of PAR.
